Online appendix for Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy

### 2020-01-24 manuscript/supplement.Rmd
Add collapsing likelihood variable info

---
title: "Supplement to Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
short-title: Supplement to Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  email: suparna.chaudhry@cnu.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
date: "`r format(Sys.time(), '%B %e, %Y')`"
title-page: false
published: 
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: true
appendix: true
---

@@

>>>>

---
title: "Online appendix for Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
short-title: Online appendix for Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  email: suparna.chaudhry@cnu.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
date: "`r format(Sys.time(), '%B %e, %Y')`"
title-page: false
published: 
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: true
appendix: true
---

@@

# Collapsing likelihood variable

To simplify our analysis, we collapse our likelihood scale from a 1-5 Likert scale to a binary variable:

```{r child = "output/tables/tbl-collapsed-likelihood.md"}
```

To check that the results are internally consistent when collapsed, we ran an ordered probit model 
(using Stan) to see if the cutpoints follow the distribution of answers, and they do. "Somewhat likely" and above has a cutpoint of > 0.18, meaning that the likelihood is positive on average for both "Somewhat likely" and "Extremely likely."

```{r child = "output/tables/tbl-probit-likelihood.md"}
```
